---
name: Jessica Streeter
position: "Data Scientist"
address: "1433 S 18th St, Philadelphia PA 19146"
phone: 631 678 7222
www: phillynerd.netlify.com
email: "jstreeter.rutgers@gmail.com"
twitter: phillynerd
github: phillynerd
linkedin: jessica-streeter-9053a630
headcolor: #f4bf42
date: "`r format(Sys.time(), '%B %Y')`"
aboutme: "Jessica is a driven, self-motivated data scientist who is passionate about issues of mental health, social justice, and socioeconomic disparities in health care. She was trained as a medical sociologist with an emphasis on mental illness, quantitative methodologies, and research methods.  She has worked in the mental health field in a variety of different capacities, including direct care and academia, since 2005."
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(googlesheets)
library(tidyverse)
library(rorcid)
#education
CVedu_key <- extract_key_from_url("https://docs.google.com/spreadsheets/d/1M3y33nzpoTKt7J_GesfTa2EE8FcRPJwGZZeBUBj1qqc/edit#gid=0")
GS_CVedu <- gs_key(CVedu_key)

CVedu<- GS_CVedu %>% 
  gs_read()

#jobs
CVjob_key <- extract_key_from_url("https://docs.google.com/spreadsheets/d/1XIKWwsRaQqRCVEzeIWFMCpin2I0Znyn1-3NLcjagS8o/edit#gid=0")
GS_CVjob <- gs_key(CVjob_key)

CVjob<- GS_CVjob %>% 
  gs_read("Jobs")

#pubs and pres
me <- as.orcid(x = "0000-0002-0576-083X")
orc_CVpub <- works(me)
```

# Skills
## Programs/Languages

* R, SQL, Rstudio, Excel, SPSS, PowerBI (limited)

## Methodologies

* cox regressions, linear/logistic regressions, clustering (k-means, knn), random forest

## Teaching

* 10+ years teaching undergraduate courses like research methods, race relations, and sociology of mental illness
* Awarded Teaching Excellence Honor Role (Rutgers, each semester); Harry C. Bredemeier Award for Career Teaching Excellence (Rutgers; 2011); and SAGE Teaching Innovations and Professional Development Award (2012)

## Leadership

* Team lead for Code4PA hackathon targetting the opioid epidemic in PA
* Created organization-wide policies around data review and documentation
* Regularly asked to do trainings and present technical materials for diverse audiences (technical, clinical, providers, and city government)

# Experience

```{r jobs}
CVjob %>% 
  arrange(Workplace, desc(as.numeric(Year_Finish))) %>% 
  detailed_entries (what = Title,
                   when = paste0(Startdate, "-", Enddate),
                   with = Workplace,
                   why = Details,
                   where = Where) 
  
```

\newpage
# Education
```{r edu}
CVedu %>% 
brief_entries(what = ifelse(is.na(Degree), Course_of_Study,
                     paste0(Course_of_Study, ": ", Degree)),
              when = Date_Complete,
              with = School) %>% 
  arrange(desc(when))


```


# Publications & Presentations
*Selected examples, orcID: [0000-0002-0576-083X](https://orcid.org/0000-0002-0576-083X)*
```{r pubs}
orc_CVpub %>% 
  arrange(desc(`publication-date.year.value`)) %>%
   mutate(type_clean = ifelse(type == "book-chapter", "Peer Reviewed Book Chapter",
          ifelse(type == "journal-article", "Journal Article",
          ifelse(type == "magazine-article", "Magazine",
          ifelse(type %in% c("conference-abstract","conference-paper"), "Conference",
          ifelse(type == "book", "Book", NA)))))) %>% 
  filter(type_clean != "Magazine") %>% 
  detailed_entries(
      with = title.title.value,
      when = `publication-date.year.value`,
      what = paste0(`journal-title.value`, ": ", type_clean)
  )

```


